---
title: "R Markdown Presentation & Plotly"
author: "Felipe Alves"
date: "7/22/2019"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(plotly))
```

## UFO Sightings Dataset

The data used in this persentation was collected from [tinyTuesday](https://github.com/rfordatascience/tidytuesday), a weekly data project in R from the R4DS online learning community.

```{r Data_Cleaning, echo = FALSE, message=FALSE}
ufo_sightings <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-06-25/ufo_sightings.csv")

ufo_sightings <- read.csv("C:/Users/efelial/Documents/Ericsson/Courses/Coursera/Data_Science-John_Hopkins/9 - Developing Data Products in R/W3/Project/ufo_sighting_data.csv")

ufo_sightings <- ufo_sightings %>% 
  rename(
    state = state.province,
    city_area = city
    )
                                 
usa <- ufo_sightings %>%
  select(country, state, city_area, latitude, longitude) %>%
  filter(country == "us") %>%
  add_count(state, name = 'state_count') %>%
  add_count(city_area, name = 'city_count') %>%
  mutate(state = toupper(state)) %>%
  mutate(city_area = toupper(city_area)) %>%
  mutate(latitude = as.numeric(as.character(latitude)))

```

## Interactive Map per State

Hover over the map below to see the amount of UFO sightings per US State.
The colors in the map also give an indication of the amount.

```{r Plot_map_per_State, echo = FALSE}
# Create data frame
state_data <- data.frame(State = usa$state, nOccurences = usa$state_count)
# Create hover text
state_data$hover <- with(state_data, paste(State, '<br>', "Occurences:", nOccurences))
# Make state borders white
borders <- list(color = toRGB("red"))
# Set up some mapping options
map_options <- list(
  scope = 'usa',
  projection = list(type = 'albers usa'),
  showlakes = TRUE,
  lakecolor = toRGB('white')
)

plot_ly(z = ~state_data$nOccurences,
        text = ~state_data$hover,
        locations = ~state_data$State,
        type = 'choropleth',
        locationmode = 'USA-states',
        color = state_data$nOccurences,
        colors = 'Blues',
        marker = list(line = borders)) %>%
  layout(title = 'US UFO sightings per State',
         geo = map_options)
```

## Bubble Map per City

The map below goes into more details on the UFO Sightings and show all cities in which a UFO was sighted more than 100 times
Each bubble's size and color is an indication of the amount of occurences.

```{r Plot_bubble_map_per_City, echo = FALSE, warning=FALSE}

# Create data frame
city_data <- data.frame(City = usa$city_area, nOccurences = usa$city_count, lat = usa$latitude, lng = usa$longitude)

# Filter data frame
city_data <- filter(city_data, nOccurences > 100)

# Create hover text
city_data$hover <- with(city_data, paste(City,'<br>',"Occurences:",nOccurences))

g <- list(
  scope = 'usa',
  projection = list(type = 'albers usa'),
  showland = TRUE,
  landcolor = toRGB("gray85"),
  subunitwidth = 1,
  countrywidth = 1,
  subunitcolor = toRGB("white"),
  countrycolor = toRGB("white")
)

plot_geo(city_data, 
         locationmode = 'USA-states', 
         sizes = c(min(city_data$nOccurences), max(city_data$nOccurences))) %>%
  add_markers(
    x = ~lng, 
    y = ~lat, 
    size = ~nOccurences, 
    color = ~nOccurences, 
    hoverinfo = "text",
    text = ~hover) %>%
  layout(
    title = 'US UFO Sightings per City<br>(Over 100 sightings)', 
    geo = g)

```

